\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
Add ipython and pygrass examples
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64931 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{

>>>>

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_sc_syntax}
}

@@

	IPython Notebook is a web-based application that provides a tool to: developing, documenting, and executing code, as well as communicating the results.
	One great tool to process and visualize your data/maps, integrating formulas and explanatory text, interacting with remote server and clusters.

	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
	\includegraphics[width=0.8\linewidth, clip, trim=0 0 0 0]{ipython_nb}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{
Some API examples to convert a raster map to a numpy array and then back to a raster.

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_raster_examples}
